### 2020-11-09 docs/manuscript/PLOS-MSc-Thesis.tex
write clearer Results section in Abstract

\subsection*{Results}
Out of 2061 GRNs selected using the genetic algorithm, 714 groups of 
topologies were found that were able to interpret a morphogen input. The 
main network motif involved in the formation of the band expression pattern 
was the type 3 Incoherent Feed Forward Loop (I3-FFL); we also present here 
other network topologies that have not been previously reported and that can 
be useful as synthetic regulatory networks due to its relatively simple design 
and robust morphogen interpretation mechanisms.

>>>>

\subsection*{Results}
Out of 2061 GRNs selected using the genetic algorithm, we found 714 groups of 
topologies that were able to interpret a morphogen input. The main network motif 
involved in the formation of the band expression pattern was the type 3 
Incoherent Feed Forward Loop (I3-FFL); we also present here other network 
topologies that have not been previously reported and that can be useful as 
synthetic regulatory networks due to its simple design and robust morphogen 
interpretation mechanisms.
